---
title: "Network-Based Pathway Enrichment Analysis in Cervical Cancer"
subtitle: "Master's Degree Project in Bioinformatics – University of Skövde"
author: "Bhavana Chowdary Kothapalli"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: flatly
    highlight: tango
    number_sections: true
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 10,
  fig.height = 7
)
set.seed(123)
```

# Overview

This R Markdown document executes the complete analysis pipeline for the
Master's thesis:

> *Network-Based Pathway Enrichment Analysis to Improve Molecular Insight
> in Cervical Cancer*

All 12 analysis scripts are sourced in sequence. Results are saved to
the `outputs/` directory.

---

# Setup: Load Libraries

```{r libraries}
library(GEOquery)
library(Biobase)
library(affy)
library(preprocessCore)
library(hgu133plus2.db)
library(AnnotationDbi)
library(limma)
library(clusterProfiler)
library(org.Hs.eg.db)
library(GOSemSim)
library(STRINGdb)
library(igraph)
library(ggplot2)
library(ggrepel)
library(pheatmap)

dir.create("outputs",         showWarnings = FALSE, recursive = TRUE)
dir.create("outputs/figures", showWarnings = FALSE, recursive = TRUE)
dir.create("outputs/tables",  showWarnings = FALSE, recursive = TRUE)
dir.create("outputs/rdata",   showWarnings = FALSE, recursive = TRUE)
```

---

# Data Acquisition

```{r data-acquisition, cache=TRUE}
source("scripts/01_data_acquisition.R")
```

---

# Quality Control

```{r quality-control, cache=TRUE}
source("scripts/02_quality_control.R")
```

---

# Normalisation

```{r normalisation, cache=TRUE}
source("scripts/03_normalization.R")
```

---

# Differential Expression Analysis

```{r differential-expression, cache=TRUE}
source("scripts/04_differential_expression.R")
```

---

# GO Enrichment Analysis

```{r go-enrichment, cache=TRUE}
source("scripts/05_go_enrichment.R")
```

---

# KEGG Pathway Enrichment

```{r kegg-enrichment, cache=TRUE}
source("scripts/06_kegg_enrichment.R")
```

---

# STRING PPI Network Construction

```{r string-network, cache=TRUE}
source("scripts/07_string_network.R")
```

---

# Network Topological Analysis

```{r network-topology, cache=TRUE}
source("scripts/08_network_topology.R")
```

---

# Hub Gene Identification

```{r hub-genes, cache=TRUE}
source("scripts/09_hub_identification.R")
```

---

# Functional Module Detection

```{r modules, cache=TRUE}
source("scripts/10_module_detection.R")
```

---

# Comparative Analysis

```{r comparative, cache=TRUE}
source("scripts/11_comparative_analysis.R")
```

---

# Final Visualisation

```{r visualisation, cache=TRUE}
source("scripts/12_visualization.R")
```

---

# Session Information

```{r session-info}
sessionInfo()
```
